Competing Bandits: The Perils of Exploration under Competition

### 2018-09-05 paper/content/barriers.tex
Fixed a compile bug: \begin{table*}[h*] -> \begin{table*}[h]
updatd tables

\section{Data and Reputation as Barriers to Entry}\label{section:6}
In the temporary monopoly setting, the incumbent firm enjoys a first
mover advantage, which allows the firm to acquire data on potentially
suboptimal actions without incurring an immediate reputational
consequence, and to build up a high reputation before the entrant
enters the market. Thus, the early entry gives the incumbent both a
\textit{data} advantage and a \textit{reputational} advantage over the
entrant. This provides a quantitative perspective on the classic
``first mover advantage" \cite{kerin1992first} in the digital economy
where data can serve as a barrier to entry in many markets.

@@

\begin{table*}[h*]
\centering
\begin{tabular}{|c|c|c|c||c|c|c|}
\hline
  & \multicolumn{3}{c|}{Information erased}
  & \multicolumn{3}{c|}{Reputation erased}\\
\hline
& $\TS$  & $\DEG$  & $\DG$ 
& $\TS$  & $\DEG$  & $\DG$
\\\hline
$\TS$ 
    & \makecell{\textbf{0.021}$\pm$0.009}
    & \makecell{\textbf{0.16}$\pm$0.02} 
    & \makecell{\textbf{0.21} $\pm$0.02} 
    %%
    & \makecell{\textbf{0.0096}$\pm$0.006}
    & \makecell{\textbf{0.11}$\pm$0.02}
    & \makecell{\textbf{0.18}$\pm$0.02} 
    \\ \hline
$\DEG$ 
    & \makecell{\textbf{0.26}$\pm$0.03} 
    & \makecell{\textbf{0.3}$\pm$0.02} 
    & \makecell{\textbf{0.26}$\pm$0.02} 
    %%
    & \makecell{\textbf{0.073}$\pm$0.01}
    & \makecell{\textbf{0.29}$\pm$0.02}
    & \makecell{\textbf{0.25}$\pm$0.02} 
    \\ \hline
$\DG$ 
    & \makecell{\textbf{0.34}$\pm$0.03} 
    & \makecell{\textbf{0.4}$\pm$0.03} 
    & \makecell{\textbf{0.33}$\pm$0.02} 
    %%
    & \makecell{\textbf{0.15}$\pm$0.02}
    & \makecell{\textbf{0.39}$\pm$0.03}
    & \makecell{\textbf{0.33}$\pm$0.02}
    \\\hline
\end{tabular}
\caption{Information-erased vs. reputation-erased experiment, on Heavy-Tail MAB instance. Each cell describes the duopoly game between the entrant's algorithm (the {\bf row}) and the incumbent's algorithm (the {\bf column}). The cell specifies the entrant's market share for the rounds in which hit was present: the average (in bold) and the 95\% confidence interval. NB: smaller average is better for the incumbent.}
\label{barrier_exp}
\end{table*}

>>>>

\section{Data and Reputation as Barriers to Entry}\label{section:6}

\begin{table*}[h]
\centering
\begin{tabular}{|c|c|c|c||c|c|c|}
\hline
  & \multicolumn{3}{c||}{Information erased}
  & \multicolumn{3}{c|}{Reputation erased}\\
\hline
& $\TS$  & $\DEG$  & $\DG$
& $\TS$  & $\DEG$  & $\DG$
\\\hline
$\TS$
    & \makecell{\textbf{0.021}$\pm$0.009}
    & \makecell{\textbf{0.16}$\pm$0.02}
    & \makecell{\textbf{0.21} $\pm$0.02}
    %%
    & \makecell{\textbf{0.0096}$\pm$0.006}
    & \makecell{\textbf{0.11}$\pm$0.02}
    & \makecell{\textbf{0.18}$\pm$0.02}
    \\ \hline
$\DEG$
    & \makecell{\textbf{0.26}$\pm$0.03}
    & \makecell{\textbf{0.3}$\pm$0.02}
    & \makecell{\textbf{0.26}$\pm$0.02}
    %%
    & \makecell{\textbf{0.073}$\pm$0.01}
    & \makecell{\textbf{0.29}$\pm$0.02}
    & \makecell{\textbf{0.25}$\pm$0.02}
    \\ \hline
$\DG$
    & \makecell{\textbf{0.34}$\pm$0.03}
    & \makecell{\textbf{0.4}$\pm$0.03}
    & \makecell{\textbf{0.33}$\pm$0.02}
    %%
    & \makecell{\textbf{0.15}$\pm$0.02}
    & \makecell{\textbf{0.39}$\pm$0.03}
    & \makecell{\textbf{0.33}$\pm$0.02}
    \\\hline
\end{tabular}
\caption{Information-erased vs. reputation-erased experiment, on Heavy-Tail MAB instance. Each cell describes the duopoly game between the entrant's algorithm (the {\bf row}) and the incumbent's algorithm (the {\bf column}). The cell specifies the entrant's market share for the rounds in which hit was present: the average (in bold) and the 95\% confidence interval. NB: smaller average is better for the incumbent.}
\label{barrier_exp}
\end{table*}

In the temporary monopoly setting, the incumbent firm enjoys a first
mover advantage, which allows the firm to acquire data on potentially
suboptimal actions without incurring an immediate reputational
consequence, and to build up a high reputation before the entrant
enters the market. Thus, the early entry gives the incumbent both a
\textit{data} advantage and a \textit{reputational} advantage over the
entrant. This provides a quantitative perspective on the classic
``first mover advantage" \cite{kerin1992first} in the digital economy
where data can serve as a barrier to entry in many markets.

@@
